\documentclass{article}

\title{OOMTK v.2}
\author{Filip Br\v ci\' c\\$<$brcha@users.sourceforge.net$>$}

\begin{document}

\maketitle

\section{Introduction}

This is the OOMTK v.2. That stands for ``Object-Oriented Multi-Tasking Kernel''.

\subsection{Design goals}

\begin{itemize}
\item Robustness
\item Binary compatibility
\item Portability
\item User-friendly and developer-friendly design
\end{itemize}

\subsection{Implementation details}

\subsubsection{Robustness}

The system is designed to run on a very small microkernel. The idea is to separate
as much things as possible from the kernel into the user-space. One of the basic
microkernel servers will be the Phoenix server. His responsibility will be to watch
the other servers and to restart them if that is needed. The kernel itself will
only be used to bootstrap the system and to start the scheduler. The kernel will then
launch the MMU and IPC servers which will be responsible for manageing the memory
and inter-process communication.

When those three servers (Phoenix, MMU and IPC) are lounched, the kernel will launch
the Init server that will handle the rest of the boot process. The system booting
will depend on GNU Grub for loading the servers. If GNU Grub is not ported to other
architectures, the kernel will get the readonly kernel filesystem to read the servers
itself.

\subsubsection{Binary compatibility}

The intent is to make the system able to run unmodified applications from other
systems, such as GNU/Linux, GNU/Hurd, FreeBSD, NetBSD, OpenBSD, Darwin, Mac OS X,
Windows, etc. For that purpose it will have separate SysCall servers that will be
launched on demand and that will translate syscalls into server requests. Since the
kernel itself is not going to handle any syscalls (it only does task switching after
bootup), the Syscall server will exist even for the native system. It will get
information about loaded servers and on request it will send their ids to other
processes. I might integrate Syscall server and Phoenix into one server since they
both have to have information about other servers, but maybe it is better left doubled
like this. This way Syscall server can act like Phoenix if Phoenix dies, or revitalize
and reinitialize Phoenix if it dies.

\section{Microkernel design}

\section{Basic servers}

\section{Additional servers}

\end{document}
